\bf $\mathsf{TEDAT}$: Boosting Bandwidth-based Availability Over Inter-DC WAN

### 2021-01-18 paper.tex
add the revisions by prof. Shi

%Conference
\acmConference[Sigcomm]{}
\acmYear{2021}
%\copyrightyear{}

@@

\begin{abstract}
Inter-DataCenter Wide Area Network (Inter-DC WAN) that connects geographically distributed data centers is becoming one of the most critical network infrastructures.
%Network failures are common in WANs, so the provision of high availability has been a major focus of network research.
Due to the limited bandwidth resources and inevitable link failures, it is highly challenging to guarantee network availability for services, especially those with stringent bandwidth demands, over inter-DC WAN.
%While modern datacenter services increasingly call for high availability, network failures in WANs remain a fairly common phenomenon.
%Most traffic engineering schemes only consider connectivity-based availability and this severely degrades quality of service, thus revenue.
We present $\mathsf{TEDAT}$,
a novel Traffic Engineering (TE)  framework that 
%contains admission control, online scheduling and failure recovery.
aims for \textit{bandwidth-based availability} provision, where a service level agreement (SLA) defines that a demand on certain bandwidth should be satisfied with a stipulated probability,  when subjected to the network capacity and possible failures of the inter-DC WAN.
%Also, $\mathsf{TEDAT}$ is able to maximize revenue when network fails.
%$\mathsf{TEDAT}$ tries to guarantee the bandwidth-based availability of demands . 
%$\mathsf{TEDAT}$ generates a probabilistic failure model from empirical data and maximizes the profit that can be achieved under certain constrains on  bandwidth-based availability. 
%For the failure model, we propose a pruning algorithm to reduce the problem size.
%For the optimization problem, we prove it is NP-hard and  propose a greedy algorithm to efficiently solve it with only minor profit loss. 
%We design and implement an SDN-based system named $\mathsf{Dionysus}$ to deploy $\mathsf{TEDAT}$ over inter-DC WAN.
The three core components of  $\mathsf{TEDAT}$, i.e., admission control, traffic scheduling and failure recovery, are built on different mathematical models and theoretically analyzed. 
They are also extensively compared against state-of-the-art TE schemes, using trace driven simulations as well as real testbed across different topologies, traffic matrices and failure scenarios. 
Our evaluation demonstrates that compared with the optimal admission strategy, $\mathsf{TEDAT}$ can speed up the online admission control by 30 $\times$ at the expense of 3\% higher rejection ratio. 
On the other hand, compared with the latest TE schemes like FFC and TEAVAR,   $\mathsf{TEDAT}$ can meet the availability SLAs of 40\% more bandwidth demands, and when network failure causes SLA violations, it can retain 30\% more profit  under a simple pricing and refunding model.
%.
% $\mathsf{TEDAT}$ can 
%(1) achieve 30 $\times$ speedup in admission control time at the expense of sacrificing 8\% in performance compared to the optimal stragety;
%(2) increase the percentage of demands that satisfy their availability SLAs by up to 40\%;
%(3) hold 30\% more profit for the provider when network fails. 
%The evaluation results demonstrate that $\mathsf{TEDAT}$ can make 20\%, 25\%, 30\%, 40\% more flows satisfy their bandwidth-based availability demands  than TEAVAR, SMORE, SWAN and FFC, respectively.
\end{abstract}

@@

\section{Introduction}
Nowadays, large scale online services such as finance trading, web search, online game and video streaming are posing stringent requirements on the availability and agility of the underlying network infrastructure, where Inter-DataCenter Wide Area Network (Inter-DC WAN) that
connects geographically distributed data centers has been playing a critical role. 
Many service providers, including Amazon, Google, Microsoft and etc., are providing various  optimizations for their global WAN, especially with the help of the emerging software-defined networking techniques \cite{swan,hong2018b4,evole,Teavar,calendaring,FFC,bwe,dynamic,SMORE,B4,OWAN}.

@@

Such negative impact on inter-DC WAN services will ultimately translate into monetary loss (e.g., refund to customers).

@@

and there are inevitable competitions over the scarce inter-DC WAN resources  \cite{swan,Guaranteeings,calendaring}.
Therefore, the design and optimization of inter-DC WANs have to take heterogeneities and competitions into consideration.

@@

In this paper, we argue that although existing traffic engineering schemes \cite{FFC,Teavar,jointfailure,R3,Stochastic,Optical,PCF} have already factored in network risks and targets for network availability guarantee, they still have three limitations when facing heterogeneous and competing bandwidth demands over inter-DC WAN:
\textit{Firstly}, some proactive schemes (e.g., FFC \cite{FFC}) need too much bandwidth headroom to guarantee  network is free from congestion when there are failures, and consequently their bandwidth allocation can often be too conservative \cite{FFC,R3,PCF} and result in inefficient resource usage as well as significant performance gap \cite{failureslarge,Teavar}.
To prevent congestion during rerouting, links, including those with negligible failure probabilities must be kept at low utilization, and this method is suited for ISP networks which are designed with worst-case assumptions about failures.
However, content providers can't invest so much in their private backbone (e.g., inter-DC WAN) as public backbone to reduce the risk of congestion  \cite{publicore},

@@

therefore, leaving too much capacity unused most of the time when no link fails over inter-DC WAN implies resource wastage.

@@

\textit{Secondly}, existing techniques (e.g., TEAVAR \cite{Teavar}) usually emphasize on network service availability rather than the availability targets of applications deployed over networks, i.e., they normally take a \textit{one-size-fit-all} approach and do not differentiate availability requirements of different classes of traffic, which may impair high availability traffic when there are competitions.

@@

Availability is one of the main items of Service Level Agreements (SLAs) \cite{amazon,azure} and cloud providers have to refund customers for any violation of SLAs.

@@

For example, Microsoft Azure should guarantee at least 99.9\% availability of the backup service and a minimum of 99.95\% availability of ExpressRoute service \cite{azure}.
If the availability agreement is violated, a 10\% or 25\% refund will return to customers.

@@

TEAVAR \cite{Teavar} can't guarantee the availability of high priority traffic when resource is inadequate.

@@

\textit{Thirdly}, their failure recovery schemes might cause much monetary loss when network fails.
In tunnel-based traffic engineering schemes (e.g., TEAVAR \cite{Teavar}, FFC \cite{FFC}),
traffic can be redistributed across the surviving tunnels via rerouting when any tunnel becomes unavailable.
Their rerouting mechanisms via surviving tunnels could lead to much revenue loss when services attempt to restore rate after failures.

%Although they consider rerouting of data plane, their random re-hashing mechanisms fail to capture link utilization and service importance, which could lead to congestion and monetary loss.
%WAN bandwidth remains a constrained resource and schemes (e.g., TEAVAR \cite{Teavar}) ignore diverse availability demands ,
%as a result, services with small availability demands will gain redundant bandwidth and affect other services' performance finally.
%Thirdly, they fail to consider the priority/urgency of different services.
%Thirdly, they lack fine grained priority description 
%In data centers, services have different urgency levels.
%For instance, the event service and the vRoute service, responsible for communication of critical components,  are of the highest level of importance, while data-backup and data-distribution are services running in the background and are of the lowest level of importance \cite{hanzhang}.\
%Although some schemes, such as SWAN \cite{swan}, allocate bandwidth in strict precedence across a small number of priority classes,
%they are too coarse and fine-grained priority description is needed. 
Facing these challenges, in this paper we make the following  \textbf{contributions}:

Firstly, we advocate traffic engineering with \textit{bandwidth-based availability guarantee} \cite{hong2018b4}: 
a tenant's \textit{promised bandwidth of service $j$ should be available at least $\beta_j\%$ time}.  
It tries to guarantee the bandwidth demands from tenants under network uncertainty.
We show that state-of-the-art traffic engineering schemes fail to meet services' bandwidth-based availability targets under arbitrarily link failures (see $\S$\ref{background}).
This is due to the fact that these schemes either ignore the difference in link failure probabilities that can vary by several orders of magnitude in practice or fail to consider the diverse availability targets of services.
%The stronger availability can impel network to provide stable services.
%Compared with the connectivity-based availability, it makes a further step and tries to guarantee the minimal bandwidth demands under network uncertainty after the success of connections.
%
%Taking the diverse availability demands from different applications and the application importance into consideration,

Secondly, we propose $\mathsf{TEDAT}$ (Traffic Engineering under Diverse Availability Targets),
a novel TE optimization framework that allows network operators to optimize bandwidth-based availability for diverse services over inter-DC WAN (see $\S$\ref{HATE}).
Compared with other TE schemes (see $\S$\ref{relate}), $\mathsf{TEDAT}$ is the first work to formally guarantee bandwidth-based availability demands from tenants in a unifying framework.

@@

$\mathsf{TEDAT}$ employs a fixed-readmission-combination allocation algorithm for online admission control to strike balance between efficiency and optimality.

@@

We prove that for demands already admitted by our algorithm, there must exist an allocation scheme to satisfy their bandwidth-based availability targets.

@@

We further propose a linear programming scheduling algorithm to allocate bandwidth for the admitted demands periodicly.
The linear programming complexity increases exponentially with network size and we propose a pruning method which cuts off the scenarios that hardly happen to effectively reduce the size.
Our online scheduling algorithm is able to guarantee diverse availability targets of services even when network resource is inadequate.

@@

$\mathsf{TEDAT}$  also pre-computes backup allocation across each tunnel to maximize revenue when a link fails.
We model the failure recovery problem as  a 0-1 Mixed-integer linear programming, prove its NP-hardness and propose a 2-approximation algorithm to solve it.

@@

Thirdly, 
we  design and implement $\mathsf{TEDAT}$ system (see $\S$\ref{system}) and conduct extensive experiments through real trace driven simulations and on a small testbed  (see $\S$\ref{evaluation}).
We compare  $\mathsf{TEDAT}$ with state-of-the-art TE schemes such as TEAVAR \cite{Teavar}, SMORE \cite{SMORE}, SWAN \cite{swan} and FFC \cite{FFC}, across different scenarios, topologies, traffic matrices.
Our evaluation demonstrates that $\mathsf{TEDAT}$ can 
(1) achieve 30 $\times$ speedup in admission control time at the expense of sacrificing 8\% in performance compared to the optimal stragety;
(2) increase the percentage of demands that satisfy their availability SLAs by up to 40\%;
(3) hold 30\% more profit for the provider when network fails. 
 %At last, we show the related works (see $\S$\ref{relate}).
%Traditionally, links are heavily underutilized to achieve a more rigorous availability target. 
%However, in reality, the failure probability of a single link can even differ by three orders of magnitude.
%Therefore, some link failure can be negligible and it makes no sense to reduce the utilization of these links.
%With the link Under TEDAT, links can maintain high utilization.

@@

How to maintain high performance is a big problem for network operators.
Frequently network failures can result in SLA violations and eventually loss of revenue to service providers \cite{riskbased,analysis-osdi,amazon,azure}.

@@

\section{Evaluation} \label{evaluation}
In this section, we evaluate the performance of $\mathsf{TEDAT}$ both in real trace driven simulation and testbed.
%We begin by describing the experimental framework ($\S$ \ref{setting}). 
We show the performance of $\mathsf{TEDAT}$ through answering the following specific questions:

 \begin{itemize}
  \item \textbf{What is the benefit of  $\mathsf{TEDAT}$ ?}
  In $\S$ \ref{testbedresults}, we show $\mathsf{TEDAT}$ proactively considers link failure probability as well as the diverse demands of services proactively and it increases the percentage of services that satisfy their availability SLAs by up to 40\%. 
  \item \textbf{How does $\mathsf{TEDAT}$ compare with the state-of-the-art traffic engineering TE schemes?} In $\S$ \ref{scales}, we show the consistent performance of  $\mathsf{TEDAT}$ under various topologies and traffic. $\mathsf{TEDAT}$ performs  up to 30\%, 40\%, 50\%, 75\% better than TEAVAR\cite{Teavar}, SMORE\cite{SMORE}, SWAN\cite{swan} and FFC\cite{FFC} on bandwidth-availability guarantee, respectively.
 \item \textbf{ How effect is  $\mathsf{TEDAT}$ under different parameter settings ?} In  $\S$ \ref{settings}, we show the stable performance of $\mathsf{TEDAT}$  framework. It doesn't depend on specific profit function, routing schemes, etc.
 \item \textbf{ How robust is the solution? } In $\S$ \ref{purning}, we evaluate the accuracy and efficiency of the solutions. The average error between the optimal and approximate solutions is within 8\% and we also show the algorithm is fast and accuracy enough to use in large scale network. 
 \end{itemize}

@@

\begin{figure}
\centering
\subfigure[Admission control]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/error.pdf}}
\subfigure[Measured and demand ratio]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/optimization_time.pdf}}
\caption{Benefits of admission control.}
\label{admission-benefit}
\end{figure}
%\begin{figure*}[t]
%\centering
%%\subfigure[Weight differentiation]{
%%\includegraphics[width=0.32\textwidth]{fig/evaluation/Geometric.pdf}}
%%\subfigure[Solution comparison]{
%%\includegraphics[width=0.32\textwidth]{fig/evaluation/version.pdf}}
%%\subfigure[Tunnel selection]{
%%\includegraphics[width=0.32\textwidth]{fig/evaluation/routing.pdf}}
%\subfigure[Profit comparison]{
%\includegraphics[width=0.32\textwidth]{fig/evaluation/fake/totalprofit.pdf}}
%\subfigure[Target satisfaction percentage]{
%\includegraphics[width=0.32\textwidth]{fig/evaluation/weight.pdf}}
%\subfigure[Availability comparison]{
%\includegraphics[width=0.32\textwidth]{fig/evaluation/fake/availability-cdf.pdf}}
%%\subfigure[Same importance]{
%%\includegraphics[width=0.24\textwidth]{fig/evaluation/sameweight.pdf}}
%\caption{Performance comparison under different metrics with IBM topology and traffic trace.}
%\label{motivatio_fig2}
%\end{figure*}

@@

Figure \ref{availability_fig1}(a)  shows $\mathsf{TEDAT}$ has only about 3\% performance gap from the optimal solution and can accept about 50\% more demands than the \textit{Fixed} consistently.
Similar to \cite{Teavar}, we next start a post-processing simulation, in which intends to send entirely bandwidth under each scenario at each time slot.
%We write down the bandwidth loss of each scenario for each demand and each scenario's corresponding probability.
The sum of scenario probability where demand is fully satisfied reflects the \textit{achieved availability}.
If a demand's achieved availability is higher than its availability target throughout duration time slots, then the availability defined in SLA is \textit{satisfication}.
Figure \ref{availability_fig1}(b) demonstrates that $\mathsf{TEDAT}$ can meet the availability SLAs of 40\% more demands than other traffic engineer algorithms.
The violation of SLA for $\mathsf{TEDAT}$ comes from demands rejection.
The reason for this is that $\mathsf{TEDAT}$ adopts admission control and it considers the diverse availability targets of different bandwidth demands.
$\mathsf{TEDAT}$ can make demands with stringent availability requirements pass links with high reliability, therefore, their availability targets can be guaranteed, but other schemes are unable differentiate demands.
To show this benefit, we adopt \textit{Fixed} admission control for each traffic scheduling algorithm and Figure \ref{availability_fig1}(c) shows the comparisons.
We can see that $\mathsf{TEDAT}$ performs at least 10\% better than other algorithms even under the same admission method.
%Satisfaction percentage. It denotes the percentages of applications whose achieved availability is larger than the corresponding target.
%Figure \ref{availability_fig1}(b) shows 
%$\mathsf{TEDAT}$ performs about 20\%, 25\%, 30\%,  40\% better than TEAVAR, SMORE, SWAN, FFC, respectively.
%%Specially, when traffic scale is 3, more than 70\% applications can satisfy their availability demands, which is at least 30\% better than TEAVAR.
%Specially, the advantage of $\mathsf{TEDAT}$  is more obvious when there are resource competition (e.g., $s=3$).
%%The reason for this is that $\mathsf{TEDAT}$ considers the bandwidth-based availability demand differentiation of applications.
%This picture also demonstrates that the performance of $\mathsf{TEDAT}$ doesn't depend on particular network topology and traffic.
%Next, we take IBM trace as the example and perform the experiments.

%\textbf{Path selection.}
%
%
% \begin{figure}
%\begin{center}
%\includegraphics [width=0.8\columnwidth] {fig/topologyutilization.pdf}
%\caption{Effect of link utilization. }
%\label{topologyutilization}
%\end{center}
%\end{figure}

%\subsubsection{Performance under different settings}\label{settings}
%%We now evaluate the performance of $\mathsf{TEDAT}$ under different settings with  IBM topology and trace.
%
%\textbf{Magnitude of weights.}
%In the previous experiments, we set weight within \{1,2,3,4,5\} to present the importance of services. 
%In this part, we evaluate the performance with different magnitude of weights.
%Figure \ref{fig-weight} shows the satisfaction fraction for the Important and Significant services under $\mathsf{TEDAT}$, when weight difference between the adjacent levels ranges from 1 to 32 (e.g., if the difference is 2, weight set is \{1,3,5,7,9\}).
%We can see that the satisfaction fraction becomes steady after increasing.
%This is because when heightening weight gap,  important services can gain more resources and meet their availability targets with high probability.
%
%%\textbf{Weight number.}
%%Five important levels are used in the experiments shown above.
%%Figure \ref{fig-weightnumber} shows the profit cumulative distribution for important applications (tail 20\%).
%%We can see that more than 80\% important applications achieve their availability targets. 
%%Specially, more important levels can benefit  those important applications.
%
%\textbf{More $\mathsf{TEDAT}$ solutions.}
%%The default  profit is 1 for applications whose availability demands are satisfied, otherwise the profit is $\mu(R_j)=0.01\times R_j$.

>>>>

%Conference
\acmConference[Submitted for review to SIGCOMM]{}
\acmYear{2021}
%\copyrightyear{}

@@

\begin{abstract}
Inter-DataCenter Wide Area Network (Inter-DC WAN) that connects geographically distributed data centers is becoming one of the most critical network infrastructures.
%Network failures are common in WANs, so the provision of high availability has been a major focus of network research.
Due to the limited bandwidth resources and inevitable link failures, it is highly challenging to guarantee network availability for services, especially those with stringent bandwidth demands, over inter-DC WAN.
%While modern datacenter services increasingly call for high availability, network failures in WANs remain a fairly common phenomenon.
%Most traffic engineering schemes only consider connectivity-based availability and this severely degrades quality of service, thus revenue.
We present $\mathsf{TEDAT}$,
a novel Traffic Engineering (TE)  framework that 
%contains admission control, online scheduling and failure recovery.
aims for \textit{bandwidth-based availability} provision, where a service level agreement (SLA) defines that a demand on certain bandwidth should be satisfied with a stipulated probability,  when subjected to the network capacity and possible failures of the inter-DC WAN.
%Also, $\mathsf{TEDAT}$ is able to maximize revenue when network fails.
%$\mathsf{TEDAT}$ tries to guarantee the bandwidth-based availability of demands . 
%$\mathsf{TEDAT}$ generates a probabilistic failure model from empirical data and maximizes the profit that can be achieved under certain constrains on  bandwidth-based availability. 
%For the failure model, we propose a pruning algorithm to reduce the problem size.
%For the optimization problem, we prove it is NP-hard and  propose a greedy algorithm to efficiently solve it with only minor profit loss. 
%We design and implement an SDN-based system named $\mathsf{Dionysus}$ to deploy $\mathsf{TEDAT}$ over inter-DC WAN.
The three core components of  $\mathsf{TEDAT}$, i.e., admission control, traffic scheduling and failure recovery, are built on different mathematical models and theoretically analyzed. 
They are also extensively compared against state-of-the-art TE schemes, using real testbed as well as trace driven simulations across different topologies, traffic matrices and failure scenarios. 
Our evaluation demonstrates that, compared with the optimal admission strategy, $\mathsf{TEDAT}$ can speed up the online admission control by 30 $\times$ at the expense of 5\% higher rejection ratio. 
On the other hand, compared with the latest TE schemes like FFC and TEAVAR,   $\mathsf{TEDAT}$ can meet the availability SLAs for 40\% more bandwidth demands, and when network failure causes SLA violations, it can retain 25\% more profit  under a simple pricing and refunding model.
%.
% $\mathsf{TEDAT}$ can 
%(1) achieve 30 $\times$ speedup in admission control time at the expense of sacrificing 8\% in performance compared to the optimal stragety;
%(2) increase the percentage of demands that satisfy their availability SLAs by up to 40\%;
%(3) hold 30\% more profit for the provider when network fails. 
%The evaluation results demonstrate that $\mathsf{TEDAT}$ can make 20\%, 25\%, 30\%, 40\% more flows satisfy their bandwidth-based availability demands  than TEAVAR, SMORE, SWAN and FFC, respectively.
\end{abstract}

@@

\section{Introduction}
Nowadays, large scale online services such as finance trading, web search, online shopping, online game and video streaming are posing stringent requirements on the availability and agility of the underlying network infrastructure, where Inter-DataCenter Wide Area Network (Inter-DC WAN) that
connects geographically distributed data centers has been playing a critical role. 
Many service providers, including Amazon, Google, Microsoft, etc., are providing various  optimizations for their global WAN, especially with the help of the emerging software-defined networking techniques \cite{swan,hong2018b4,evole,Teavar,calendaring,FFC,bwe,dynamic,SMORE,B4,OWAN}.

@@

Such negative impacts on inter-DC WAN services will ultimately translate into monetary loss (e.g., refund to customers).

@@

there are inevitable competitions over the scarce inter-DC WAN bandwidth  \cite{swan,Guaranteeings,calendaring}.
Therefore, the design and optimization of inter-DC WANs have to take competitions, heterogeneities and economic interests into consideration.

@@

In this paper, we argue that although existing traffic engineering schemes \cite{FFC,Teavar,R3,swan,PCF,B4,SMORE} have already factored in network risks and aimed for network availability guarantee, they can't meet the above objectives due to three limitations:
% when facing heterogeneous and competing bandwidth demands over inter-DC WAN:
\textit{First}, most of them \cite{FFC,R3,PCF,Teavar,SMORE} typically make a conservative bandwidth allocation, so that even if a failure occurs, surviving paths are used and the network can still be free from congestion under traffic rerouting.
%when there are failures, and consequently their bandwidth allocation can often be too conservative \cite{FFC,R3,PCF} and result in inefficient resource usage as well as significant performance gap \cite{failureslarge,Teavar}.
To prevent congestion, links, including those with negligible failure probabilities, must be kept at low utilization, 
resulting in significant waste of network bandwidth (and potentially less accommodated users). 
Such a solution may be fit for existing ISP networks which use over provision to avoid congestion, but for new players, such as content providers that are building their own backbone network (either physically \cite{B4,swan,amazon,evole} or leasing bandwidth from ISPs \cite{cato, aryaka}), this is quite uneconomic \cite{publicore}. 
%and this method is suited for ISP networks which are designed with worst-case assumptions about failures.
%However, content providers can't invest so much in their private backbone (e.g., inter-DC WAN) as public backbone to reduce the risk of congestion  \cite{publicore},

@@

%therefore, leaving too much capacity unused most of the time when no link fails over inter-DC WAN implies resource wastage.

@@

\textit{Second}, existing techniques mainly focus on the availability of network reachability, but ignore that users not only have diverse demands on bandwidth,  but also ask for different levels of reliability. Providing reliable bandwidth can be a value-added service for many cloud providers, typically in the form 
%(e.g., TEAVAR \cite{Teavar}) usually emphasize on network service availability rather than the availability targets of applications deployed over networks, i.e., they normally take a \textit{one-size-fit-all} approach and do not differentiate availability requirements of different classes of traffic, which may impair high availability traffic when there are competitions.

@@

%Availability is one of the main items of 
Service Level Agreements (SLAs) \cite{amazon,azure}.
%and cloud providers have to refund customers for any violation of SLAs.

@@

For example, Microsoft Azure  guarantees at least 99.9\% availability for backup service and 99.95\% availability for ExpressRoute service \cite{azure}.
If the availability agreement is violated, a 10\% or 25\% refund will be returned to the customers.
A \textit{one-size-fit-all} approach \cite{Teavar} ignoring these heterogeneities cannot support such SLAs well, and and may even hurt critical and uninterruptible applications when there are competitions on bandwidth. 

@@

%TEAVAR \cite{Teavar} can't guarantee the availability of high priority traffic when resource is inadequate.

@@

\textit{Third}, 
such heterogeneities and competitions are also not considered by current failure recovery approaches, especially those who allocate bandwidth aggressively \cite{Teavar,swan}. 
They may run into congestions when rerouting traffic under network failures. 
Such violations of SLAs will inevitably cause revenue loss, which should be reduced as much as possible.

%their failure recovery schemes might cause much monetary loss when network fails.
%In tunnel-based traffic engineering schemes (e.g., TEAVAR \cite{Teavar}, FFC \cite{FFC}),
%traffic can be redistributed across the surviving tunnels via rerouting when any tunnel becomes unavailable.
%Their rerouting mechanisms via surviving tunnels could lead to much revenue loss when services attempt to restore rate after failures.

%Although they consider rerouting of data plane, their random re-hashing mechanisms fail to capture link utilization and service importance, which could lead to congestion and monetary loss.
%WAN bandwidth remains a constrained resource and schemes (e.g., TEAVAR \cite{Teavar}) ignore diverse availability demands ,
%as a result, services with small availability demands will gain redundant bandwidth and affect other services' performance finally.
%Thirdly, they fail to consider the priority/urgency of different services.
%Thirdly, they lack fine grained priority description 
%In data centers, services have different urgency levels.
%For instance, the event service and the vRoute service, responsible for communication of critical components,  are of the highest level of importance, while data-backup and data-distribution are services running in the background and are of the lowest level of importance \cite{hanzhang}.\
%Although some schemes, such as SWAN \cite{swan}, allocate bandwidth in strict precedence across a small number of priority classes,
%they are too coarse and fine-grained priority description is needed. 
To solve these challenges, in this paper we make the following  three \textbf{contributions}:

Firstly, we advocate traffic engineering with \textit{bandwidth-based availability} (BA) provision: 
a BA demand $(d, \beta, \alpha, \gamma)$ means that it requests bandwidth $d$ for a life duration between $\alpha$ and $\gamma$, and should be ensured in at least a fraction $\beta$ of the duration, subjected to the network capacity and possible failures. Such a demand is typically represented by a Service Level Agreement (see Table \ref{target} for real world examples), and different users or applications may pose different demands. 
%a tenant's \textit{promised bandwidth of service $j$ should be available at least $\beta_j\%$ time}.  
%It tries to guarantee the bandwidth demands from tenants under network uncertainty.
We show that state-of-the-art traffic engineering schemes fail to the heterogeneous bandwidth-based availability demands in an economic manner, especially under diverse link failure probabilities that may vary by several orders of magnitude (see $\S$\ref{background}).
%meet services' bandwidth-based availability targets under arbitrarily link failures (see $\S$\ref{background}).
%This is due to the fact that these schemes either ignore the difference in link failure probabilities that can vary by several orders of magnitude in practice or fail to consider the diverse availability targets of services.
%The stronger availability can impel network to provide stable services.
%Compared with the connectivity-based availability, it makes a further step and tries to guarantee the minimal bandwidth demands under network uncertainty after the success of connections.
%
%Taking the diverse availability demands from different applications and the application importance into consideration,

Secondly, we design $\mathsf{TEDAT}$,
a novel traffic engineering  framework that aims for bandwidth based availability provision over inter-DC WAN (see $\S$\ref{HATE}).
$\mathsf{TEDAT}$ is composed of three core components, i.e., admission control, traffic scheduling and failure recovery. 
The admission control scheme 

@@

$\mathsf{TEDAT}$ strikes balance between efficiency and optimality, so that new demands can be admitted and guaranteed as much as possible with negligible delay.

@@

%We prove that for demands already admitted by our algorithm, there must exist an allocation scheme to satisfy their bandwidth-based availability targets.

@@

Then based on a linear programming model, our traffic scheduling algorithm sets up tunnels and allocates bandwidth for the admitted demand.
To cope with the complexity which increases exponentially with network size,  we further propose a pruning method by ignoring certain failure scenarios that hardly happen.
At last, based on a mixed-integer linear programming model, the failure recovery procedure pre-computes backup bandwidth allocations and reroute traffic to minimize the revenue loss due to SLA violations, and is proved to be 2-optimal. 
%Our online scheduling algorithm is able to guarantee diverse availability targets of services even when network resource is inadequate.

@@

%$\mathsf{TEDAT}$  also pre-computes backup allocation across each tunnel to maximize revenue when a link fails.
%We model the failure recovery problem as  a 0-1 Mixed-integer linear programming, prove its NP-hardness and propose a 2-approximation algorithm to solve it.

@@

Thirdly, 
we implement $\mathsf{TEDAT}$ as a real system, including a centralized controller and multiple brokers (one for each DC),  together with end-host clients (see $\S$\ref{system}).
 We conduct extensive experiments using real trace driven simulations as well as  on a small testbed  (see $\S$\ref{evaluation}).
We compare  $\mathsf{TEDAT}$ with state-of-the-art TE schemes such as TEAVAR \cite{Teavar}, SMORE \cite{SMORE}, SWAN \cite{swan}, B4 \cite{B4} and FFC \cite{FFC}, across different topologies, traffic matrices and failure scenarios.
Our evaluation demonstrates that $\mathsf{TEDAT}$ can 
(1) speed up the online admission control by 30 $\times $ at the expense of 5\% higher rejection ratio;
(2) meet the availability SLAs for 40\% more bandwidth demands;
(3) retain 25\% more profit when network failure causes SLA violations, under a simple pricing and refunding model. 
To our knowledge, $\mathsf{TEDAT}$ is the first to tackle bandwidth based availability provision over inter-DC WAN, where heterogeneities of demands and link failures are systematically taken into account for profit maximization.  
 %At last, we show the related works (see $\S$\ref{relate}).
%Traditionally, links are heavily underutilized to achieve a more rigorous availability target. 
%However, in reality, the failure probability of a single link can even differ by three orders of magnitude.
%Therefore, some link failure can be negligible and it makes no sense to reduce the utilization of these links.
%With the link Under TEDAT, links can maintain high utilization.

@@

How to maintain high performance is a big problem for network operators.
Frequent network failures can result in SLA violations and eventually loss of revenue to service providers \cite{riskbased,analysis-osdi,amazon,azure}.

@@

\section{Evaluation} \label{evaluation}
In this section, we evaluate the performance of $\mathsf{TEDAT}$  in both real trace driven simulation and testbed.
Our main results are as follows.

%We begin by describing the experimental framework ($\S$ \ref{setting}). 
%We show the performance of $\mathsf{TEDAT}$ through answering the following specific questions:
(1)  The admission control of $\mathsf{TEDAT}$ can achieve a reasonable tradeoff. $\mathsf{TEDAT}$ can speed up the online admission control by 30 $\times$ at the expense of 5\% higher rejection ratio.

%compared with the latest TE schemes like FFC and TEAVAR, TEDAT can meet the availability SLAs of 40% more bandwidth demands, and when network failure causes SLA violations, it can retain 30% more profit under a simple pricing and refunding model.
(2) $\mathsf{TEDAT}$ has consistent performance under various topologies and traffic.
Compared with the state-of-the-art traffic engineering algorithms, $\mathsf{TEDAT}$ is able to make  40\% more bandwidth demands meet availability SLAs.

(3) $\mathsf{TEDAT}$ can retain 30\% more profit when network fails.

(4)  $\mathsf{TEDAT}$ is fast and accuracy.
The average error of traffic scheduling is within 8\% and the profit loss of greedy algorithm is less than 10\%.

% \begin{itemize}
%  \item \textbf{What is the benefit of  $\mathsf{TEDAT}$ ?}
%  In $\S$ \ref{testbedresults}, we show $\mathsf{TEDAT}$ proactively considers link failure probability as well as the diverse demands of services proactively and it increases the percentage of services that satisfy their availability SLAs by up to 40\%. 
%  \item \textbf{How does $\mathsf{TEDAT}$ compare with the state-of-the-art traffic engineering TE schemes?} In $\S$ \ref{scales}, we show the consistent performance of  $\mathsf{TEDAT}$ under various topologies and traffic. $\mathsf{TEDAT}$ performs  up to 30\%, 40\%, 50\%, 75\% better than TEAVAR\cite{Teavar}, SMORE\cite{SMORE}, SWAN\cite{swan} and FFC\cite{FFC} on bandwidth-availability guarantee, respectively.
% \item \textbf{ How effect is  $\mathsf{TEDAT}$ under different parameter settings ?} In  $\S$ \ref{settings}, we show the stable performance of $\mathsf{TEDAT}$  framework. It doesn't depend on specific profit function, routing schemes, etc.
% \item \textbf{ How robust is the solution? } In $\S$ \ref{purning}, we evaluate the accuracy and efficiency of the solutions. The average error between the optimal and approximate solutions is within 8\% and we also show the algorithm is fast and accuracy enough to use in large scale network. 
% \end{itemize}

@@

%\begin{figure*}[t]
%\centering
%%\subfigure[Weight differentiation]{
%%\includegraphics[width=0.32\textwidth]{fig/evaluation/Geometric.pdf}}
%%\subfigure[Solution comparison]{
%%\includegraphics[width=0.32\textwidth]{fig/evaluation/version.pdf}}
%%\subfigure[Tunnel selection]{
%%\includegraphics[width=0.32\textwidth]{fig/evaluation/routing.pdf}}
%\subfigure[Profit comparison]{
%\includegraphics[width=0.32\textwidth]{fig/evaluation/fake/totalprofit.pdf}}
%\subfigure[Target satisfaction percentage]{
%\includegraphics[width=0.32\textwidth]{fig/evaluation/weight.pdf}}
%\subfigure[Availability comparison]{
%\includegraphics[width=0.32\textwidth]{fig/evaluation/fake/availability-cdf.pdf}}
%%\subfigure[Same importance]{
%%\includegraphics[width=0.24\textwidth]{fig/evaluation/sameweight.pdf}}
%\caption{Performance comparison under different metrics with IBM topology and traffic trace.}
%\label{motivatio_fig2}
%\end{figure*}

@@

Figure \ref{availability_fig1}(a)  shows $\mathsf{TEDAT}$  rejects only about 3\% more demands than the optimal solution and can accept about 50\% more demands than the \textit{Fixed} consistently.
Similar to \cite{Teavar}, we next start a post-processing simulation, in which intends to send entirely bandwidth under each scenario at each time slot.
%We write down the bandwidth loss of each scenario for each demand and each scenario's corresponding probability.
The sum of scenario probability where demand is fully satisfied reflects the \textit{achieved availability}.
%If a demand's , then the availability defined in SLA is \textit{satisfaction}.
The term \textit{satisfaction percentage} refers to the fraction of total arrival demands whose achieved availability are higher than their availability targets throughout duration.
Figure \ref{availability_fig1}(b) demonstrates that $\mathsf{TEDAT}$ can make 40\% more demands satisfy SLA availability.
%Demands SLA violation of  $\mathsf{TEDAT}$ mainly comes from admission control rejection.
%The reason for this is that $\mathsf{TEDAT}$ adopts admission control and it considers the diverse availability targets of different bandwidth demands.
$\mathsf{TEDAT}$ can make demands with stringent availability requirements pass links with high reliability, therefore, their availability targets can be guaranteed, but other schemes are unable differentiate demands.
To show this benefit, we adopt \textit{Fixed} admission control for each traffic scheduling algorithm, then Figure \ref{availability_fig1}(c) shows $\mathsf{TEDAT}$ performs at least 10\% better than other algorithms under the \textit{Fixed} admission control method.
Figure \ref{availability_fig1}(d) shows the average monetary gain percentage for the scenario in which one failure could occur in the network.
We can see $\mathsf{TEDAT}$  is able to retain 30\% more profit than other algorithms when network fails.
\begin{figure}
\centering
\subfigure[Cutoff error]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/error.pdf}}
\subfigure[Optimization time]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/optimization_time.pdf}}
\caption{Impact of pruning for traffic scheduling.}
\label{availability_fig3}
\end{figure}
We qualify the scalability by measuring the admission control time for each demand.
The simulation is performed on a Linux server (4-core, 2.60GHz processor with 32GB).
As shown in Figure \ref{admission-benefit}, the admission control time of $\mathsf{TEDAT}$ is less than 1s with about less than 5\% error, which is at least 30$\times$ faster the global optimal solution under ATT topology.
Algorithm \ref{pruning} cuts off the scenarios that can hardly happen.
